\LARGE \bf Steering a Swarm Using Global Inputs and Swarm Statistics

### 2016-08-15 journalSwarmControl/experiment.tex
Made fig 1 smaller, no captions

To design the policy, we first discretize the environment. 
In \cite{ShahrokhiIROS2015}, we used breadth-first search (BFS) on this discretized grid to determine $\mathbf{M}_{BFS}$, the shortest distance from any grid cell to the goal, and generated a gradient map $\nabla \mathbf{M}$  shown in Fig.~\ref{fig:BFSGradient}.  
The object's center of mass is at $\mathbf{b}$ and has average radius $r_b$, so we define the desired direction for the object as $\mathbf{D}(\mathbf{b}) = \nabla \mathbf{M}(\mathbf{b})$. 
The robots were directed behind the object at  $\mathbf{b} - 1.5 r_b \mathbf{D}(\mathbf{b})$, then directed to  $\mathbf{b} - 0.1 r_b \mathbf{D}(\mathbf{b})$ to push the object toward the goal location. However, BFS has no penalties on object collisions with obstacles, and the resulting collisions made the BFS solution slow.

 To avoid obstacles, this paper models object movement as a Markov Decision Process (MDP) with non-deterministic movement.  
  Value iteration,  as described in \cite{Thrun2005}, is used to learn an \emph{optimal policy}: a function that assigns a control input to every possible state.
 At each state the object can be commanded to move in one of eight directions with a small probability of moving in a wrong direction.

>>>>

To design the policy, we first discretize the environment. 
In \cite{ShahrokhiIROS2015}, we used breadth-first search (BFS) on this discretized grid to determine $\mathbf{M}_{BFS}$, the shortest distance from any grid cell to the goal, and generated a gradient map $\nabla \mathbf{M}$  shown in Fig.~\ref{fig:BFSGradient}.  
The object's center of mass is at $\mathbf{b}$ and has average radius $r_b$, so we define the desired direction for the object as $\mathbf{D}(\mathbf{b}) = \nabla \mathbf{M}(\mathbf{b})$. 
The robots were directed behind the object at  $\mathbf{b} - 1.5 r_b \mathbf{D}(\mathbf{b})$, then directed to  $\mathbf{b} - 0.1 r_b \mathbf{D}(\mathbf{b})$ to push the object toward the goal location. 
This approach using workspace BFS fails to account for the hull of the object and will suggest moves that can cause at least partial collision with the workspace. A configuration-space BFS approach avoids that problem but still fails to model uncertain actuation of the object by the swarm.

To solve both these problems, this paper models object movement as a Markov Decision Process (MDP) with non-deterministic movement.  
  Value iteration,  as described in \cite{Thrun2005}, is used to learn an \emph{optimal policy}: a function that assigns a control input to every possible state.
 At each state the object can be commanded to move in one of eight directions with a small probability of moving in a wrong direction.
